Quantifying and Modeling Global Water Accessibility including Water Typology

### 2021-01-26 docs/manuscript/manuscript.tex
Contribution first paragraph.

\section{Contribution}

\citet{jagalsDoesImprovedAccess2006} highlights in a case study in a rural area in South Africa discovered providing small communities. The rural area used untreated river water as their water source. The Researchers installed good quality water with a piped distribution system and increase accessibility by installing communal taps. However, this implementation did not fall within the parameters of safe water. This didn't increase household quantities, which remained around 18 L per person per day. Their research
gives a potential understanding even making the drinking water accessible might not improve the quality of the water
itself.

@@

\begin{figure}[h!]
  \centering
  \includegraphics[width=.7\textwidth]{centroid}
  \caption{Centroid of the Four Cluster Groupings}
  \label{fig:centroid}
\end{figure}
\begin{figure}[h!]
  \centering
  \includegraphics[width=1\textwidth]{typology}
  \caption{Cluster Typology Average of Water Accessibility Variables }
  \label{fig:typology}
\end{figure}
\begin{figure}[h!]
\raggedright
  \includegraphics[width=1.25\textwidth]{dendrogram}
  \caption{Cluster Dendrogram with Four Cuts}
  \label{fig:dendrogram}
\end{figure}

@@

Cluster C consists of 20 countries mostly in central Africa, some in west Africa and one country in the pacific islands. Cluster C countries are grouped by their cluster typology factor for largest for Water 30 minutes or less away round trip, second largest typology factor of Public tap/standpipe, and third largest typology factor of Water more than 30 minutes away round trip. Example country members are Angola, Burundi, Central African Republic.

%

>>>>

\section{Contribution}
Lack of water accessibility is a major crisis for many vulnerable people around the world. We have determined to seek literature reviews from the past 15 years to have the most up to date information because information on water accessibility is a topic that is constantly changing throughout the world due to different international, government, and even local policies. The literature review intends to investigate different journal articles on water accessibility in a global scale. Therefore we can conduct a research to fill many major gaps  to analyze the water accessibility predictor variables which could increase and enhance water accessibility in global scale. We will always gain new insight and wisdom on information about water accessibility through the global scale as we investigate and determine literature reviews chronologically. 
\citet{jagalsDoesImprovedAccess2006} highlights in a case study in a rural area in South Africa discovered providing small communities. The rural area used untreated river water as their water source. The Researchers installed good quality water with a piped distribution system and increase accessibility by installing communal taps. However, this implementation did not fall within the parameters of safe water. This didn't increase household quantities, which remained around 18 L per person per day. Their research
gives a potential understanding even making the drinking water accessible might not improve the quality of the water
itself.

@@

\begin{figure}[h!]
  \centering
  \includegraphics[width=.7\textwidth]{centroid}
  \caption{Centroid of the Four Cluster Groupings}
  \label{fig:centroid}
\end{figure}
\begin{figure}[h!]
  \centering
  \includegraphics[width=1\textwidth]{typology}
  \caption{Cluster Typology Average of Water Accessibility Variables }
  \label{fig:typology}
\end{figure}
\begin{figure}[h!]
\raggedright
  \includegraphics[width=1.15\textwidth]{dendrogram}
  \caption{Cluster Dendrogram with Four Cuts}
  \label{fig:dendrogram}
\end{figure}

@@

Cluster C consists of 20 countries mostly in central Africa, some in west Africa and one country in the pacific islands. Cluster C countries are grouped by their cluster typology factor for largest for Water 30 minutes or less away round trip, second largest typology factor of Public tap/standpipe, and third largest typology factor of Water more than 30 minutes away round trip as shown in \autoref{fig:spider} and \autoref{fig:typology}. Example country members are Angola, Burundi, Central African Republic.

Cluster D consists of 22 geographically dispersed countries. Cluster D countries are categorized by their cluster typology factor for rainwater compared to the other cluster typology. Additionally, the highest factor was Piped into dwelling, but is still lower than the Cluster B as shown in \autoref{fig:spider} and \autoref{fig:typology}. Example country members are Azerbaijan, Bolivia, and Cambodia.
